
\thispagestyle{empty}
\clearpage

\vspace*{\stretch{2}}

\begin{center}
  \textbf{Acknowledgements}\\[0.75cm]

  \begin{minipage}{0.9\textwidth}
    \setlength{\parskip}{0.45em}
There are lots of people I am grateful for. Here are some select highlights.

First of all, I'd like to acknowledge the EPSRC for making this entire thing financially viable. Spending over $20$ years in formal education is simultaneously a badge of honour but also a source of crippling pain. Because of you, EPSRC, I've been able to enjoy the experience of not paying council tax until my mid-to-late twenties. The downside of this arrangement is my grandparents have been asking, with minimal optimism, ``Jack, are you \emph{ever} going to get a job?''.

A massive thank you to my PhD supervisors, Kevin Wilson and Daniel Henderson. Without the pair of you this thesis would be littered with typos are \emph{even more} of my bad jokes. Kevin, I've enjoyed our many, excessively long conversations about the way statistics should be done. I'm not sure if anyone else really agrees with us. Daniel, thank you for keeping me \emph{and Kevin} on track.

To everyone who has held a desk in PhD 4, it's been good (apart from chaotic bit where going in the office was banned). It would be unjust if I did not recognise Jack as a door sign aficionado and the world's most effective rubber duck.

I'd also like to thank my friends in the Royal Statistical Society, especially the Young Statisticians, for reminding me that statistics is something I actually enjoy, even when this thesis has convinced me otherwise.

My friends outside of statistics should also be mentioned. I am grateful that you have pretended to be interested in my thesis, doing a PhD becomes an annoying personally trait which is hard to shake off. Jack, Tom, I have always assumed that ``massive nerd'' is a term of endearment.

Finally, Aim\'ee, thank you for everything you have done for me. Putting up with me being in a right strop on many occasions for reasons such as my code crashing for the fifth time in as many hours, or because reviewer 2 has been particularly unforgiving. Without your love and support this would have been much more difficult.

  \end{minipage}

\end{center}

\vspace*{\stretch{3}}

\cleardoublepage
